Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-11-06 analysis/paper/paper.Rmd
Update figures and remove old figures

p1 <- ggplot(data = RAW_data,
             aes(
               x = DAI,
               y = TShB_incidence
             )) +
  geom_text(
    data = p1_anot,
     mapping = aes(x = x,
                   y = y,
                   label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = WMGT,
               linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = WMGT,
               shape = WMGT)) +
  scale_y_continuous(
    labels = function(x)
      paste0(x * 100),
    limits = c(0, 1),
    name = "Tiller Incidence (%)"
  ) +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "Irrigation",
       shape = "Irrigation") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = c(x = 0.065, y = 0.76),
    legend.background = element_rect(
      color = "black",
      size = 0.5,
      linetype = "solid"
    ),
    axis.title.x = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_text(face = "bold")
  )

@@

p4 <- ggplot(data = RAW_data,
             aes(
               x = DAI,
               y = TShB_incidence
             )) +
  geom_text(
    data = p4_anot,
    mapping = aes(x = x,
                  y = y,
                  label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = NRTE,
                   linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = NRTE,
                   shape = NRTE)) +
  scale_y_continuous(
    labels = function(x)
      paste0(x * 100),
    limits = c(0, 1),
    name = "Tiller Incidence (%)"
  ) +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Rate",
       shape = "N Rate") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = c(x = 0.1,
                        y = 0.7),
    legend.background = element_rect(
      color = "black",
      size = 0.5,
      linetype = "solid"
    ),
    axis.title.x = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_text(face = "bold")
  ) +
  guides(linetype = guide_legend(ncol = 2),
         shape = guide_legend(ncol = 2))

>>>>

p1 <- ggplot(data = RAW_data,
             aes(
               x = DAI,
               y = TShB_incidence
             )) +
  geom_text(
    data = p1_anot,
     mapping = aes(x = x,
                   y = y,
                   label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = WMGT,
               linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = WMGT,
               shape = WMGT)) +
  scale_y_continuous(
    labels = function(x)
      paste0(x * 100),
    limits = c(0, 1),
    name = "Tiller Incidence (%)"
  ) +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "Irrigation",
       shape = "Irrigation") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = c(x = 0.068, y = 0.76),
    legend.background = element_rect(
      color = "black",
      size = 0.5,
      linetype = "solid"
    ),
    axis.title.x = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_text(face = "bold")
  )

@@

p4 <- ggplot(data = RAW_data,
             aes(
               x = DAI,
               y = TShB_incidence
             )) +
  geom_text(
    data = p4_anot,
    mapping = aes(x = x,
                  y = y,
                  label = label)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = NRTE,
                   linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = NRTE,
                   shape = NRTE)) +
  scale_y_continuous(
    labels = function(x)
      paste0(x * 100),
    limits = c(0, 1),
    name = "Tiller Incidence (%)"
  ) +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Rate",
       shape = "N Rate") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "black"),
    legend.position = c(x = 0.11,
                        y = 0.7),
    legend.background = element_rect(
      color = "black",
      size = 0.5,
      linetype = "solid"
    ),
    axis.title.x = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_text(face = "bold")
  ) +
  guides(linetype = guide_legend(ncol = 2),
         shape = guide_legend(ncol = 2))
